---
title: "Time to Event"
description: "Kaplan-Meier cumulative incidence with the endpoint composed live from multiselect event filters, pointwise 95% bands, censor marks and an at-risk table."
index: 12
output:
  html_document:
    code_folding: hide
    includes:
      before_body: util/example-chrome.html
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
source("util/example-page.R")
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleHeader())
```

Kaplan-Meier curves for an endpoint the reviewer composes rather than one someone derived in advance. The multiselect filters over the event records decide which events qualify — every treatment-emergent event by default, and one click away the serious-only endpoint or a body-system basket. The module then takes each participant's first qualifying event by onset day, censors everyone else at their follow-up-end day, and draws the product-limit estimator with Greenwood log-log pointwise 95% bands, censor marks, and the at-risk and cumulative-event tables beneath the axis. Cumulative incidence (1 − KM, rising) is the default orientation because that is the safety convention; the survival orientation is a control away. The chart below is live — rendered by the safety.viz `timeToEvent` module.

**Two data frames, and why neither can be inferred from the other.** There is no pre-derived time-to-event dataset here, because the endpoint is not fixed: `dfResults` carries the event records and `dfPopulation` carries one row per participant with the day their follow-up ended. The population frame is the denominator. A participant with no qualifying event has not dropped out of the analysis — they are censored at their own follow-up day, which the events alone cannot tell you. Records that cannot be used are counted and exportable rather than dropped silently.

**A note on the demo data.** The bundled `adae` extract carries one all-blank placeholder row per participant with no adverse events, so that the adverse-event renderers' denominator covers the whole safety population. Those rows are not events, and this chart takes its denominator from `adsl` instead, so the example drops them.

## Render this report from a workflow

The same chart ships as a gsm-idiom report workflow. Run it with `gsm.core::RunWorkflow()` to produce a standalone HTML report, or use the matching runner script:

```{r, eval = FALSE, class.source = "fold-show"}
lWorkflow <- yaml::read_yaml(
  system.file("workflow", "4_modules", "time_to_event.yaml", package = "gsm.safety")
)

dfAE <- ExampleData("adae")

gsm.core::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = list(
    dfResults = dfAE[nzchar(dfAE$AEDECOD), ],
    dfPopulation = ExampleData("adsl")
  )
)
```

```sh
Rscript inst/examples/time-to-event.R <output-dir>
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleWorkflow("time_to_event.yaml"))
```

## The live chart

```{r}
library(gsm.safety)

dfAE <- ExampleData("adae")
dfResults <- dfAE[nzchar(dfAE$AEDECOD), ]
dfPopulation <- ExampleData("adsl")

Widget_TimeToEvent(
  dfResults,
  dfPopulation,
  lSettings = list(
    endpoint_label = "Time to first treatment-emergent adverse event",
    event_filters = list(
      list(value_col = "AEBODSYS", label = "Body System"),
      list(value_col = "AEDECOD", label = "Preferred Term"),
      list(value_col = "AESER", label = "Serious"),
      list(value_col = "AESEV", label = "Severity")
    ),
    filters = list(
      list(value_col = "ARM", label = "Treatment Group")
    )
  )
)
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleFooter())
```
