---
title: "AE Explorer Workflow"
author: "gsm.safety Example"
description: "Interactive AE Explorer report rendered by running the workr YAML workflow."
index: 2
date: "`r format(Sys.time(), '%B %d, %Y %H:%M:%S %Z', tz = 'America/New_York')`"
output: html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This example runs the AE Explorer report through the same `workr` YAML workflow
that a tester or downstream package can execute directly:
`inst/workflow/3_reports/ae_explorer.yaml`. The YAML stores `meta$widgetSettings`,
calls `safetyCharts::init_aeExplorer()`, then saves the initialized widget as a
standalone HTML report with `gsm.safety::RenderSafetyChartsWidget()`.

```{r}
workflow_path <- system.file(
  "workflow", "3_reports", "ae_explorer.yaml",
  package = "gsm.safety"
)
if (!nzchar(workflow_path)) {
  workflow_path <- file.path("inst", "workflow", "3_reports", "ae_explorer.yaml")
}

lWorkflow <- yaml::read_yaml(workflow_path)
lData <- gsm.safety::MakeExampleData()
```

The workflow YAML is the report contract. It maps GSM workflow data into the
`safetyCharts` AE Explorer shape, initializes the widget with
`safetyCharts::init_aeExplorer()`, and writes the rendered HTML report with the generic renderer.

```{r}
cat(paste(readLines(workflow_path, warn = FALSE), collapse = "\n"))
```

Run the workflow with the example mapped data:

```{r}
lReport <- workr::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = lData,
  bReturnResult = TRUE
)

lReport$path
```

```{r, echo = FALSE}
lReport$widget
```
