---
title: "Histogram"
author: "gsm.safety Example"
description: "Interactive lab-results distributions with normal-range overlays, grouped small multiples, and a linked participant listing."
index: 1
output:
  html_document:
    code_folding: hide
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

<div class="example-nav" aria-label="Example navigation" style="display: flex; justify-content: space-between; gap: 1rem; margin: 0.75rem 0 1.25rem 0;">
<a class="btn btn-outline-secondary btn-sm" href="Example_AeTimelines.html">&larr; Previous: AE Timelines</a>
<a class="btn btn-outline-secondary btn-sm" href="Example_ShiftPlot.html">Next: Shift Plot &rarr;</a>
</div>

Interactive lab-results distributions with normal-range overlays, grouped small multiples, and a linked participant listing. The chart below is live — rendered by the safety.viz `histogram` module on the package's example data, with the full control sidebar.

```{r}
library(gsm.safety)

dfResults <- ExampleData("adbds")

Widget_Histogram(
  dfResults,
  lSettings = list(
    filters = list(
      list(value_col = "SITEID", label = "Site ID"),
      list(value_col = "SEX", label = "Sex"),
      list(value_col = "RACE", label = "Race"),
      list(value_col = "ARM", label = "Treatment Group"),
      list(value_col = "USUBJID", label = "Participant ID")
    ),
    groups = list(
      list(value_col = "SITE", label = "Site"),
      list(value_col = "SEX", label = "Sex"),
      list(value_col = "RACE", label = "Race"),
      list(value_col = "ARM", label = "Treatment Group")
    ),
    display_normal_range = TRUE,
    annotate_bin_boundaries = TRUE,
    test_normality = TRUE,
    group_by = "ARM",
    compare_distributions = TRUE
  ),
  height = "800px"
)
```

## Render this report from a workflow

The same chart ships as a gsm-idiom report workflow. Run it with `gsm.core::RunWorkflow()` to produce a standalone HTML report, or use the matching runner script:

```{r, eval = FALSE}
lWorkflow <- yaml::read_yaml(
  system.file("workflow", "3_reports", "safety_histogram.yaml", package = "gsm.safety")
)

gsm.core::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = list(dfResults = ExampleData("adbds"))
)
```

```sh
Rscript inst/examples/histogram.R <output-dir>
```
