---
title: "Participant Profile"
description: "The standalone drill-down for a named cohort: demographics header, standardized labs over time, adverse-event tracks on the same axis, and a measure table with sparklines."
index: 13
output:
  html_document:
    code_folding: hide
    includes:
      before_body: util/example-chrome.html
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
source("util/example-page.R")
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleHeader())
```

The drill-down that answers "what happened to this person" in one pass: a header carrying the participant's demographics and R ratio, a labs-over-time spaghetti standardized to multiples of the upper limit of normal or of baseline with per-measure reference cutpoints, adverse-event tracks drawn on that same study-day axis so a rash and a bilirubin rise line up, and a measure table whose sparklines expand into an inset. A cohort of more than one participant is ranked worst-first and stepped through. The profile below is live — rendered by the safety.viz `participantProfile` module.

**This is the standalone surface, and it is not the only one.** The same profile already mounts inside several charts: the eDISH hepatic safety explorer, the histogram and the outlier explorer each put it in a rail beside the chart, driven by whatever the reviewer selects there, through their `profile` setting. Reach for that one when someone is exploring. Reach for this one when the report already knows its cohort — a per-participant appendix, a narrative for a set of flagged participants, a listing that stands on its own page.

**Naming the cohort is not optional.** The module's standalone mount listens for a `participantsSelected` event, and nothing in a static R report dispatches one. Given no cohort it renders its controls and waits, indefinitely. So `chrParticipants` is a widget argument, delivered through the module's public programmatic-selection path — the same path the event listener takes. In a live report that list comes from a flagging metric; here it is three participants of the pilot study.

## Render this report from a workflow

The same profile ships as a gsm-idiom report workflow. Run it with `gsm.core::RunWorkflow()` to produce a standalone HTML report, or use the matching runner script:

```{r, eval = FALSE, class.source = "fold-show"}
lWorkflow <- yaml::read_yaml(
  system.file("workflow", "4_modules", "participant_profile.yaml", package = "gsm.safety")
)

dfAE <- ExampleData("adae")

gsm.core::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = list(
    dfResults = ExampleData("adbds"),
    dfAE = dfAE[nzchar(dfAE$AEDECOD), ],
    chrParticipants = c("01-701-1015", "01-701-1023", "01-701-1028")
  )
)
```

```sh
Rscript inst/examples/participant-profile.R <output-dir>
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleWorkflow("participant_profile.yaml"))
```

## The live profile

```{r}
library(gsm.safety)

dfResults <- ExampleData("adbds")
dfAE <- ExampleData("adae")

Widget_ParticipantProfile(
  dfResults,
  chrParticipants = c("01-701-1015", "01-701-1023", "01-701-1028"),
  dfAE = dfAE[nzchar(dfAE$AEDECOD), ],
  lSettings = list(
    studyday_col = "VISITNUM",
    measure_values = list(
      ALT = "Alanine Aminotransferase",
      AST = "Aspartate Aminotransferase",
      TB = "Bilirubin",
      ALP = "Alkaline Phosphatase"
    ),
    details = list(
      list(value_col = "ARM", label = "Treatment Group"),
      list(value_col = "SEX", label = "Sex"),
      list(value_col = "RACE", label = "Race")
    )
  )
)
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleFooter())
```
