---
title: "Shift Plot"
author: "gsm.safety Example"
description: "Baseline-versus-comparison shifts for each participant, with visit and summary-stat controls."
index: 2
output:
  html_document:
    code_folding: hide
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

<style>
.main-container {
  max-width: min(1700px, 96vw) !important;
}
div.html-widget {
  width: 100% !important;
  height: auto !important;
  min-height: 480px;
}
.example-nav a { text-decoration: none; }
</style>

<div class="example-nav" aria-label="Example navigation" style="display: flex; justify-content: space-between; gap: 1rem; margin: 0.75rem 0 1.25rem 0;">
<a class="btn btn-outline-secondary btn-sm" href="Example_Histogram.html">&larr; Previous: Histogram</a>
<a class="btn btn-outline-secondary btn-sm" href="Example_DeltaDelta.html">Next: Delta-Delta &rarr;</a>
</div>

Baseline-versus-comparison shifts for each participant, with visit and summary-stat controls. The chart below is live — rendered by the safety.viz `shiftPlot` module on the package's example data, with the full control sidebar.


## Render this report from a workflow

The same chart ships as a gsm-idiom report workflow. Run it with `gsm.core::RunWorkflow()` to produce a standalone HTML report, or use the matching runner script:

```{r, eval = FALSE}
lWorkflow <- yaml::read_yaml(
  system.file("workflow", "3_reports", "safety_shift_plot.yaml", package = "gsm.safety")
)

gsm.core::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = list(dfResults = ExampleData("adbds"))
)
```

```sh
Rscript inst/examples/shift-plot.R <output-dir>
```

## The live chart

```{r}
library(gsm.safety)

dfResults <- ExampleData("adbds")

Widget_ShiftPlot(
  dfResults,
  lSettings = list(
    filters = list(
      list(value_col = "SITEID", label = "Site ID"),
      list(value_col = "SEX", label = "Sex"),
      list(value_col = "RACE", label = "Race"),
      list(value_col = "ARM", label = "Treatment Group")
    ),
    baseline_visits = list("Baseline"),
    comparison_visits = list("Week 26")
  )
)
```
