---
title: "Hepatic Safety Explorer"
description: "eDISH scatter of peak liver measures with Hy's Law quadrants and participant drill-down to standardized values by study day."
index: 8
output:
  html_document:
    code_folding: hide
    includes:
      before_body: util/example-chrome.html
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
source("util/example-page.R")
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleHeader())
```

The chart below is live — rendered by the safety.viz `hepExplorer` module on the package's example data, with the full control sidebar. `measure_values` maps the ALT/AST/TB/ALP keys onto this dataset's measure names, and the visit sequence stands in for study day.

## Render this report from a workflow

The same chart ships as a gsm-idiom report workflow. Run it with `gsm.core::RunWorkflow()` to produce a standalone HTML report, or use the matching runner script:

```{r, eval = FALSE, class.source = "fold-show"}
lWorkflow <- yaml::read_yaml(
  system.file("workflow", "3_reports", "hep_explorer.yaml", package = "gsm.safety")
)

gsm.core::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = list(dfResults = ExampleData("adbds"))
)
```

```sh
Rscript inst/examples/hep-explorer.R <output-dir>
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleWorkflow("hep_explorer.yaml"))
```

## The live chart

```{r}
library(gsm.safety)

dfResults <- ExampleData("adbds")

Widget_HepExplorer(
  dfResults,
  lSettings = list(
    studyday_col = "VISITNUM",
    visit_col = "VISIT",
    visitn_col = "VISITNUM",
    measure_values = list(
      ALT = "Alanine Aminotransferase",
      AST = "Aspartate Aminotransferase",
      TB = "Bilirubin",
      ALP = "Alkaline Phosphatase"
    ),
    filters = list(
      list(value_col = "SEX", label = "Sex"),
      list(value_col = "ARM", label = "Treatment Group")
    ),
    groups = list(
      list(value_col = "ARM", label = "Treatment Group"),
      list(value_col = "SEX", label = "Sex")
    )
  )
)
```

```{r, echo = FALSE, results = "asis"}
cat(ExampleFooter())
```
