---
title: "AE Explorer"
author: "gsm.safety Example"
description: "Interactive AE Explorer report rendered from mapped GSM safety data."
index: 1
date: "`r format(Sys.time(), '%B %d, %Y %H:%M:%S %Z', tz = 'America/New_York')`"
output:
  html_document:
    code_folding: hide
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

<style>
.example-nav {
  position: sticky;
  top: 4.5rem;
  z-index: 20;
  display: flex;
  justify-content: space-between;
  gap: 1rem;
  margin: 0.75rem 0 1.25rem 0;
  padding: 0.5rem 0;
  background: var(--bs-body-bg, #fff);
  border-bottom: 1px solid var(--bs-border-color, #dee2e6);
}
.example-nav a {
  text-decoration: none;
}
.example-nav .example-nav-spacer {
  flex: 1 1 auto;
}
</style>

<div class="example-nav" aria-label="Example navigation">
<span class="example-nav-spacer"></span>
<a class="btn btn-outline-secondary btn-sm" href="Example_AE_Explorer_Workflow.html">Next: AE Explorer Workflow →</a>
</div>

This example renders the interactive AE Explorer report artifact from a small
mapped subject/adverse-event data set. The widget settings are read from the
same workflow YAML used by the `workr` example.

```{r}
workflow_path <- system.file(
  "workflow", "3_reports", "ae_explorer.yaml",
  package = "gsm.safety"
)
if (!nzchar(workflow_path)) {
  workflow_path <- file.path("inst", "workflow", "3_reports", "ae_explorer.yaml")
}

lWorkflow <- yaml::read_yaml(workflow_path)
lData <- gsm.safety::MakeExampleData()
aeData <- list(
  dm = lData$Mapped_SUBJ,
  aes = lData$Mapped_AE
)

initialized <- safetyCharts::init_aeExplorer(
  data = aeData,
  settings = lWorkflow$meta$widgetSettings
)

lReport <- gsm.safety::RenderSafetyChartsWidget(
  lInitialized = initialized,
  strWidgetName = "aeExplorer",
  strOutputDir = tempdir(),
  strOutputFile = "ae_explorer_example"
)

lReport$path
```

```{r, echo = FALSE, out.width = "95%", out.height = "700px"}
lReport$widget
```
