---
title: "Safety Histogram Workflow"
author: "gsm.safety Example"
description: "Interactive Safety Histogram report rendered by running the workr YAML workflow."
index: 22
date: "`r format(Sys.time(), '%B %d, %Y %H:%M:%S %Z', tz = 'America/New_York')`"
output:
  html_document:
    code_folding: hide
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This example runs the Safety Histogram report through a `workr` YAML workflow:
`inst/workflow/3_reports/safety_histogram.yaml`. The YAML stores the widget settings,
initializes the widget when a safetyCharts `init_*` helper is available, and
writes the rendered HTML report with `gsm.safety::RenderSafetyChartsWidget()`.

```{r}
workflow_path <- system.file(
  "workflow", "3_reports", "safety_histogram.yaml",
  package = "gsm.safety"
)
if (!nzchar(workflow_path)) {
  workflow_path <- file.path("inst", "workflow", "3_reports", "safety_histogram.yaml")
}

lWorkflow <- yaml::read_yaml(workflow_path)
lData <- gsm.safety::MakeExampleData()
```

The workflow YAML is the report contract:

<details>
<summary>Workflow YAML</summary>

```{r, echo = FALSE, results = "asis"}
writeLines(c("```yaml", readLines(workflow_path, warn = FALSE), "```"))
```

</details>

Run the workflow with the example mapped data:

```{r}
lReport <- workr::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = lData,
  bReturnResult = TRUE
)

lReport$path
```

```{r, echo = FALSE, out.width = "95%", out.height = "700px"}
lReport$widget
```
