---
title: "QT Safety Explorer"
author: "gsm.safety Example"
description: "QT/QTc central tendency against the ICH E14 threshold, outlier scatter, and categorical summaries of participants crossing the 450/480/500 ms boundaries."
index: 9
output:
  html_document:
    code_folding: hide
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

<style>
.main-container {
  max-width: min(1700px, 96vw) !important;
}
div.html-widget {
  width: 100% !important;
  height: auto !important;
  min-height: 480px;
}
.example-nav a { text-decoration: none; }
</style>

<div class="example-nav" aria-label="Example navigation" style="display: flex; justify-content: space-between; gap: 1rem; margin: 0.75rem 0 1.25rem 0;">
<a class="btn btn-outline-secondary btn-sm" href="Example_HepExplorer.html">&larr; Previous: Hepatic Safety Explorer</a>
<a class="btn btn-outline-secondary btn-sm" href="Example_Histogram.html">Next: Histogram &rarr;</a>
</div>

QT/QTc cardiac safety across three linked views. The chart below is live — rendered by the safety.viz `qtExplorer` module on the package's example ECG data, with the full control sidebar.

- **Central tendency** — mean change from baseline (Δ) by visit and arm, and, when `placebo_arm` is set, the placebo-corrected change (ΔΔ) with confidence intervals against the ICH E14 10 ms threshold of regulatory concern.
- **Outliers** — a scatter of absolute values against change from baseline, with the 450 / 480 / 500 ms and 30 / 60 ms category boundaries drawn in.
- **Categorical** — counts and rates of participants crossing each of those boundaries, by arm.

The bundled `adeg` dataset uses the ADaM ADEG column names the module expects (`TEST`, `STRESN`, `BASE`, `ARM`, plus `VISIT`/`VISITNUM`/`ABLFL`), so the chart initializes with no settings at all; the settings below name the placebo arm to unlock the ΔΔ view and add subgroup filters.

This is safety.viz **QT Explorer Phase 1**. QTcI, PR/QRS intervals, participant drill-down, and hysteresis plots are Phase 2 work, tracked upstream.

**A note on the demo data.** `adeg` comes from the CDISC Pilot 01 ECG data, which — like plenty of real trial data — is internally inconsistent: it collects RR and heart rate as separate measurements, and the two contradict each other (they were generated independently, so only 0.8% of readings agree). The QTc values here are therefore cleaned at ingestion rather than taken from the source's own pre-derived parameters: `QTcF = QT / (RR/1000)^(1/3)` and `QTcB = QT / (RR/1000)^(1/2)`, correcting against the RR implied by the recorded heart rate, which is the more credible of the two inputs. See [safety.viz#79](https://github.com/jwildfire/safety.viz/issues/79) for the full working.

Even so, the pilot's *measured* QT intervals are long for a resting population (median 444 ms), so QTcF centres near 468 ms and a majority of participants cross the 450 / 480 / 500 ms categories below. No correction formula can address that — it is a property of the synthetic source, not of the chart. The views exercise every threshold, but the crossing rates here should not be read as clinically typical.

## Render this report from a workflow

The same chart ships as a gsm-idiom report workflow. Run it with `gsm.core::RunWorkflow()` to produce a standalone HTML report, or use the matching runner script:

```{r, eval = FALSE}
lWorkflow <- yaml::read_yaml(
  system.file("workflow", "3_reports", "qt_explorer.yaml", package = "gsm.safety")
)

gsm.core::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = list(dfResults = ExampleData("adeg"))
)
```

```sh
Rscript inst/examples/qt-explorer.R <output-dir>
```

## The live chart

```{r}
library(gsm.safety)

dfResults <- ExampleData("adeg")

Widget_QtExplorer(
  dfResults,
  lSettings = list(
    placebo_arm = "Placebo",
    filters = list(
      list(value_col = "SEX", label = "Sex"),
      list(value_col = "RACE", label = "Race"),
      list(value_col = "SITE", label = "Site")
    )
  )
)
```
