---
title: "AE Timelines"
author: "gsm.safety Example"
description: "Per-participant adverse-event timelines colored by severity, with seriousness highlighting and filters."
index: 6
output:
  html_document:
    code_folding: hide
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

<style>
.main-container {
  max-width: min(1700px, 96vw) !important;
}
div.html-widget {
  width: 100% !important;
  height: auto !important;
  min-height: 480px;
}
.example-nav a { text-decoration: none; }
</style>

<div class="example-nav" aria-label="Example navigation" style="display: flex; justify-content: space-between; gap: 1rem; margin: 0.75rem 0 1.25rem 0;">
<a class="btn btn-outline-secondary btn-sm" href="Example_OutlierExplorer.html">&larr; Previous: Outlier Explorer</a>
<a class="btn btn-outline-secondary btn-sm" href="Example_AeExplorer.html">Next: AE Explorer &rarr;</a>
</div>

Per-participant adverse-event timelines colored by severity, with seriousness highlighting and filters. The chart below is live — rendered by the safety.viz `aeTimelines` module on the package's example data, with the full control sidebar.


## Render this report from a workflow

The same chart ships as a gsm-idiom report workflow. Run it with `gsm.core::RunWorkflow()` to produce a standalone HTML report, or use the matching runner script:

```{r, eval = FALSE}
lWorkflow <- yaml::read_yaml(
  system.file("workflow", "3_reports", "ae_timelines.yaml", package = "gsm.safety")
)

gsm.core::RunWorkflow(
  lWorkflow = lWorkflow,
  lData = list(dfResults = ExampleData("adae"))
)
```

```sh
Rscript inst/examples/ae-timelines.R <output-dir>
```

## The live chart

```{r}
library(gsm.safety)

dfResults <- ExampleData("adae")

Widget_AeTimelines(
  dfResults,
  lSettings = list(
    color = list(
      value_col = "AESEV",
      label = "Severity"
    ),
    highlight = list(
      value_col = "AESER",
      label = "Serious Event",
      value = "Y"
    ),
    filters = list(
      list(value_col = "AESER", label = "Serious Event"),
      list(value_col = "AESEV", label = "Severity"),
      list(value_col = "ARM", label = "Treatment Group"),
      list(value_col = "USUBJID", label = "Participant ID")
    ),
    details = list(
      list(value_col = "AEBODSYS", label = "Body System"),
      list(value_col = "AEDECOD", label = "Dictionary-Derived Term")
    ),
    sort_participants = "earliest"
  )
)
```
